---
title: "CCN Analyses 2025"
output: html_document
---


```{r}
library("tidyverse")
library("dplyr")
library("ggplot2")
library(ggthemes)
library(langcog)
library(lme4)
library(lmerTest)
library(here)
```

Load CSV file with fixation similarity values & get object-level averages 
```{r}
simVals = read.table(file=here::here("data/preprocessed/fixEmbedSimilarityValuesAcrossSubs.csv"),header = TRUE, sep = ",")
simVals$GazeBlock <- as.factor(simVals$GazeBlock)

# copied this from bria
simVals <- simVals %>%
  ungroup() %>%
  mutate(ObjectID = fct_reorder(ObjectID, FixSimVal))

simValsWithAvg <- simVals %>%
  group_by(ObjectID, GazeBlock) %>%
  multi_boot_standard(col = 'FixSimVal')

simValsFiltered <- filter(simVals,FixNum <11)
```


I tried normalizing fixation number within trials, and you still see the interaction in the lmer -- not perfect but I think reassuring?
```{r}
simVals <- simVals %>%
  group_by(GazeBlock, SubjectID, ObjectID) %>%
  mutate(FixNumNormalized = scale(FixNum))
```

```{r}
between_subs_sim_model <- lmer(FixSimVal ~ GazeBlock * FixNum + (GazeBlock|ObjectID) + (GazeBlock|SubjectID), simVals) #simValsFiltered
summary(between_subs_sim_model)
```

```{r}
between_subs_sim_model <- lmer(FixSimVal ~ GazeBlock * FixNum + (GazeBlock|ObjectID) + (GazeBlock|SubjectID), simVals) #simValsFiltered
summary(between_subs_sim_model)
```


```{r}
simValsByFix <- simVals %>%
  group_by(FixNum, ObjectID, GazeBlock) %>%
  mutate(num_subs = length(unique(SubjectID))) %>%
  filter(num_subs > 11) %>%
  filter(FixNum<20) %>%
  group_by(GazeBlock, SubjectID) %>%
  multi_boot_standard(col = 'FixSimVal') 
```

```{r}
ggplot(data=simValsByFix, aes(x=GazeBlock, y=scale(mean), col=SubjectID)) +
  # geom_pointrange(aes(y=mean, ymin=ci_lower, ymax=ci_upper), alpha=.2) +
  geom_point(aes(y=mean), alpha=1) +
  geom_line(aes(group=SubjectID)) +
  theme_few() +
  theme(legend.position='none') +
  ylab('Average similarity across participants (a.u.)') +
  xlab('Block')
```

```{r}
ggplot(data=simValsByFix, aes(x=FixNum, y=mean_sim_val, col=GazeBlock, size=num_subs)) +
  geom_point(alpha=.1) +
  geom_smooth(aes(group=GazeBlock,weight=num_subs), alpha=.01, method='lm') 
  # facet_wrap(~ObjectID)

```


This helps you look at predicted vs actual values from your models in R
```{r}
# simVals$predicted <- predict(between_subs_sim_model)
```


This is the raw data plots we were looking at
```{r}
ggplot(data=simVals, aes(x=FixNum, y=FixSimVal, col=GazeBlock)) +
  geom_point(alpha=.2) +
  facet_wrap(~ObjectID)
```

Looking at object level variability with CIs across subjects
```{r}
simValsbyObject <- simVals %>%
  group_by(GazeBlock, FixNum, ObjectID) %>%
  multi_boot_standard(col='FixSimVal')

simValsbySubject <- simVals %>%
  group_by(GazeBlock, FixNum, SubjectID) %>%
  summarize()
  multi_boot_standard(col='FixSimVal')
```

These kinds of averages really don't pan out -- you need the interaction with time...
```{r}
simValsbySubject <- simVals %>%
  group_by(GazeBlock, SubjectID) %>%
  filter(FixNum<20) %>%
  summarize(mean_sim_val = mean(FixSimVal)) %>%
  group_by(GazeBlock) %>%
  multi_boot_standard(col='mean_sim_val') 
```

Here's what I put in the channnel
```{r}
ggplot(simValsbyObject, aes(x=FixNum, y=mean, col=GazeBlock)) +
  geom_pointrange(aes(y=mean, ymin=ci_lower, ymax=ci_upper), alpha=.2) +
  geom_smooth(alpha=.1, method='lm') +
  theme_few() +
  facet_wrap(~ObjectID) +
  ylab('Similarity of Fixated Content') +
  xlab('Fixation number')
```

Same plot now for individual subjects
```{r}
ggplot(simValsbySubject, aes(x=FixNum, y=mean, col=GazeBlock)) +
  geom_pointrange(aes(y=mean, ymin=ci_lower, ymax=ci_upper), alpha=.2) +
  geom_smooth(alpha=.1, method='lm') +
  theme_few() +
  facet_wrap(~SubjectID) +
  ylab('Similarity of Fixated Content') +
  xlab('Fixation number')
```

Here's the raw data by subject plots
```{r}
ggplot(data=simVals, aes(x=FixNum, y=FixSimVal, col=GazeBlock)) +
  geom_point(alpha=.2) +
  facet_wrap(~SubjectID)
```

What happens if we only look at the first N fixations? (Here I picked 5)
```{r}
simVals = read.table("fixEmbedSimilarityValuesFirst5.csv",header = TRUE, sep = ",")
simVals$GazeBlock <- as.factor(simVals$GazeBlock)

# copied this from bria
simVals <- simVals %>%
  ungroup() %>%
  mutate(ObjectID = fct_reorder(ObjectID, FixSimVal))

simValsWithAvg <- simVals %>%
  group_by(ObjectID, GazeBlock) %>%
  multi_boot_standard(col = 'FixSimVal')
```


```{r}

ggplot(data=simVals, aes(x=fct_reorder(ObjectID,FixSimVal), y=FixSimVal, color = GazeBlock, fill = GazeBlock)) +
      geom_point(alpha=.1, position = position_dodge(width=.8)) + 
      geom_pointrange(data=simValsWithAvg, aes(x=(ObjectID), y=mean, ymin = ci_lower, ymax=ci_upper, color = GazeBlock), position = position_dodge(width=.8)) +
      theme_few() +
      # ylim(0,800) +
      # facet_wrap(~GazeBlock)
      theme(axis.text.x=element_text(angle = 65,hjust=1)) +
    theme(legend.position='none') +
    xlab('Individual Subjects') +
   ylab('Mean fixation count')

```



